Generating Simulated Data

### 2021-04-09 docs/SimData.Rmd
maybe equal bins are best?

  #range gives initial default binwidth, all equal (range/Nbins)
  bindef <- (Lmax-Lmin)/Nsizebins

@@

  thresh <- 0.05
  which(cumprod(rep(1, Lmax)*exp(-vonBk)) < thresh) #gives lengths of fast growth

>>>>

  #range gives initial default binwidth, all equal (range/Nbins)
  #or should it be max/nbins?
  #can use if no K estimated
  bindef <- (Lmax-Lmin)/Nsizebins

  #minmaxvonBK$BTS_fall_allbox_effic1 %>% group_by(species) %>% mutate(bindef = (maxlen)/5)

@@

  thresh <- 0.05
  which(cumprod(rep(1, Lmax)*exp(-vonBk)) > thresh) #gives 1 cm increments of fast growth?

  #
